\chapter{Results}

\section{Trigonometric moments}

\subsection{Evaluation of parameters}

Add the results from the tests I ran back in April - which combination of number of moments, Warp/NonWarp and Mirror/NonMirror techniques is the most optimal. Also mention that we do not want to use complex moments as it doubles the space needed which will be unusable for the optimizer in the Implementation section. 

\begin{table}[t]
	\centering
	\begin{tabular}{crrrrrrrr}
		\toprule
		\multirow{4}{*}{Moments} &
		\multicolumn{8}{c}{Methods} \\
		\cmidrule(lr){2-9}
		&\multicolumn{2}{c}{M\&W} &
		\multicolumn{2}{c}{M\&nonW} &
		\multicolumn{2}{c}{nMW} &
		\multicolumn{2}{c}{nMnW}\\
		\cmidrule(lr){2-9}
		& Avg & Max & Avg & Max & Avg & Max & Avg & Max \\
		\cmidrule(lr){1-9}
		1&21.3&91.19&26.4&99.44&6.54&42.93&13.24&60.23\\
		2&1.65&15.09&15.43&68.06&2.13&17.51&3.7&17.5\\
		3&0.86&5.6&9.93&55.67&1.13&6.87&0.95&5.3\\
		4&0.54&2.98&4.19&23.53&0.97&4.35&0.48&1.96\\
		5&0.34&2.22&1.19&5.68&0.75&3.37&0.31&0.97\\
		6&0.29&2.17&0.77&2.38&0.55&2.46&0.22&0.99\\
		7&0.28&2.03&0.77&1.86&0.51&1.83&0.22&1.0\\
		8&0.26&1.95&0.62&1.43&0.47&1.67&0.21&1.05\\
		9&0.24&1.81&0.4&1.28&0.43&1.68&0.22&1.04\\
		10&0.24&1.75&0.24&0.96&0.42&1.69&0.22&1.02\\
		11&0.23&1.7&0.22&1.11&0.42&1.69&0.21&1.03\\
		12&0.22&1.64&0.24&1.05&0.4&1.53&0.21&1.05\\
		13&0.22&1.6&0.24&1.0&0.38&1.4&0.22&1.04\\
		14&0.22&1.54&0.22&0.99&0.38&1.37&0.22&1.05\\
		15&0.22&1.46&0.21&1.04&0.34&2.4&0.22&1.05\\
		\bottomrule
	\end{tabular}
\caption{this is 1976, not 2000 due to discontinuities when using gradients}
\end{table}

\subsection{Reconstruction results}
Try the reconstruction on various spectrum values, also add the respective RGB values.

It might be nice to also add the ideal coefficients that we got from the borgtool by optimizing and comparing them to the coefficient that were originally computed (these are different mainly due to rounding errors during the algorithm). 

\section{Spectral uplifting}

Not really sure about the subsections here (I still don't understand the texture options).

The idea that currently comes to mind: For each parameter setting, create a record containing the following: 

- performance (time)

- average accuracy (targetRGB-latticeRGB)

- maxDifference (the important quantity)

- maybe other stuff (e.g. number of optimizer rounds)

Also mention that it is multi-threaded and performance is not really a priority - the cube has to be created only once and then can be reused as much as the artists need.

Compare these records with regard to:

\subsection{Choice of threshold}

E.g. which threshold is still good enough for the moment method, the performance etc.

\subsection{Sigmoid vs Moment method}

Compare these two approaches (the texture option which I'm not sure about), choose the same threshold for both of them, maybe do this for more thresholds?

\subsection{Constrained input}

Compare maybe the performance of different atlases, or maybe atlas vs. seeding from the middle?

The Results chapter is just a sketch and it may be completely changed, depending on the results and which of them will be interesting.

